ICT-Specific Investment Shocks and Economic Fluctuations \bigskip \\ \normalsize{Evidence and Theory of a General-Purpose Technology}

### 2019-03-07 Latex/Conference_Modena_March2019/Brianti Gati March 2019.tex
presentation with Laura comments

In this paper we focus on the \textbf{slowdown in TFP},
\begin{itemize}
	\item[$\Rightarrow$] Which variable actually boosted productivity in the last three decades? Why? 
\end{itemize}

@@

		However, as showed by Oliner et al. (2007) and Jorgerson et al. (2008), TFP have started slowing down \textbf{before} the crisis.
		\begin{itemize}
			\item[$\Rightarrow$] R\&D cannot be the full story
		\end{itemize}

@@

	\begin{enumerate}
		\item We identify ICT investment shocks using \textbf{SVAR} techniques
		\begin{itemize}
			\item A contemporaneous increase in ICT investment leads to delayed, persistent, and large rise in productivity
             \item Historical decomposition confirms that the doc-com crash explains most of the slowdown in TFP since 2006 
		\end{itemize}

@@

		\item We analyze a \textbf{general equilibrium model} to rationalize our empirical findings 
		\begin{itemize}
		\item Our identified shocks can be interpreted as supply shocks specific to the ICT sector
         \item ICT capital goods boosts productivity of ICT users thorugh a positive externality
\begin{itemize}
\item[$\Rightarrow$] The effectiveness of ICT depends on its own level of diffusion
\end{itemize}
		\end{itemize}
	\end{enumerate}

@@

\item \textbf{Resulness Checks} 
\begin{itemize}
	\item[-] Controlling for news shocks \`a la Barsky and Sims
	\item[-] Controlling for other shocks estimated via narrative approach
\end{itemize}
\item[$\Rightarrow$]  ICT shocks are \textbf{not confounded} with other shocks
\end{itemize}

@@

We extend and analyze a 2-sector GE model in the spirit of Greenwood et al. (2007). Two main assumptions are in place,
\begin{itemize}
\item[1.] Second sector specifically produce ICT durable goods to be used as inputs in both sectors' production function
\item[2.] Agents fail to internalize that productivity of both sectors positively depends of the overall ICT diffusion in the economy
\end{itemize}

@@

\item The fall in ICT investment during the doc-com crash has the right timing to rationalize the structural break in TFP
\end{itemize}

@@

>>>>

In this paper we focus on the \textbf{slowdown in TFP},
\begin{itemize}
	\item[$\Rightarrow$] Which variable boosted productivity in the last three decades? 
\item[$\Rightarrow$] Can this variable explain its recent slowdown?
\end{itemize}

@@

		However, as showed by Oliner et al. (2007) and Jorgenson et al. (2008), TFP have started slowing down \textbf{before} the crisis.
		\begin{itemize}
			\item[$\Rightarrow$] R\&D cannot be the full story
		\end{itemize}

@@

	\begin{enumerate}
		\item We identify ICT investment shocks using \textbf{SVAR} techniques
		\begin{itemize}
			\item A contemporaneous increase in ICT investment leads to a delayed, persistent, and large rise in productivity
             \item Historical decomposition confirms that the dot-com crash explains most of the slowdown in TFP since 2006 
		\end{itemize}

@@

		\item We analyze a \textbf{general equilibrium model} to rationalize our empirical findings 
		\begin{itemize}
		\item Our identified shocks can be interpreted as supply shocks specific to the ICT sector
         \item ICT capital boosts productivity of ICT users through a positive externality
\begin{itemize}
\item[$\Rightarrow$] The effectiveness of ICT depends on its own level of diffusion
\end{itemize}
		\end{itemize}
	\end{enumerate}

@@

\item \textbf{Rebustness Checks} 
\begin{itemize}
	\item[-] Controlling for news shocks \`a la Barsky and Sims
	\item[-] Controlling for other shocks estimated via narrative approach
\end{itemize}
\item[$\Rightarrow$]  ICT shocks are \textbf{not confounded} with other shocks
\end{itemize}

@@

We extend and analyze a 2-sector GE model in the spirit of Greenwood et al. (2000). Two main assumptions are in place,
\begin{itemize}
\item[1.] Second sector specifically produces ICT durable goods to be used as inputs in both sectors' production function
\item[2.] Agents fail to internalize that productivity of both sectors positively depends of the overall ICT diffusion in the economy
\end{itemize}

@@

\item The fall in ICT investment during the dot-com crash has the right timing to rationalize the structural break in TFP
\end{itemize}

@@

\frame{\frametitle{IRF Matching}

\begin{columns}[t]
\column{.3\textwidth}
\centering
\includegraphics[width=4cm,height=3.5cm]{fig_ICT_Shock_on_TFP_IRmatching_together}\\
\bigskip
\includegraphics[width=4cm,height=3.5cm]{fig_ICT_Shock_on_C_IRmatching_together} 
\column{.3\textwidth}
\centering
\includegraphics[width=4cm,height=3.5cm]{fig_ICT_Shock_on_ICTI_IRmatching_together}\\
\bigskip
\includegraphics[width=4cm,height=3.5cm]{fig_ICT_Shock_on_RP_IRmatching_together}
\end{columns}
